An in-depth study of Explainability and Adversarial Robustness in RNNs

### 2019-11-25 ex3/paper/paper.tex
Change abstract

With the rise of ubiquitous \gls{ml} systems, malicious actors have been catching up quickly to find new ways to exploit them for profit. Recently developed \gls{aml} techniques focus on computer vision and their applicability to network traffic is not straightforward: Network traffic is not only sequential but there are also many constraints that have to be considered when attacking/defending an \gls{ml}-based Intrusion Detection System. For example, attackers can only modify certain features to evade detection and certain features, like packet interarrival time cannot become less than zero. We show that already the first couple of packets of a flow are of crucial importance and are likely going to be targeted by attackers. As a countermeasure we develop an easy-to-use training procedure and can confirm that it significantly and successfully reduces the attack surface.

>>>>

With the rise of ubiquitous \gls{ml} systems, malicious actors have been catching up quickly to find new ways to exploit them for profit. Recently developed explainability and \gls{aml} techniques focus on computer vision and their applicability to network traffic is not straightforward: Network packets expose fewer features than an image, are sequential and impose several constraints on their features: For example, destination ports cannot be modified since that could impair communication. We extend existing explainability techniques and propose new ones, specifically crafted for sequential data. Applying them shows that already the first couple of packets of a communication flow are of crucial importance and are likely going to be targeted by attackers. As a countermeasure we develop an easy-to-use adversarial training procedure and can confirm that it significantly and successfully reduces the attack surface.
